---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# UltraSpoofR

The goal of UltraSpoofR is to modify the typical workflow such that the raw genuine data can be disconnected from the bulk of the workflow. It will do this by providing a new data object, which has an authenticated link to the actual data, along with a data dictionary to describe that data and a reasonable spoof of that data. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


## TODOs

Add in regex case insensitivity to type argument of the anticiapator dict --TODO
Add in Metadata dictionary interaction and functionality: likely involving big update to megametadata --TODO
introduce data spoofing elements to mimic data types with random data --TODO
constrain the spoof generation to the features of the underlying data, min max, type combos etc --TODO
