---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# UltraSpoofR

The goal of UltraSpoofR is to modify the typical workflow such that the raw genuine data can be disconnected from the bulk of the workflow. It will do this by providing a new data object, which has an authenticated link to the actual data, along with a data dictionary to describe that data and a reasonable spoof of that data. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


## TODOs

Add in regex case insensitivity to type argument of the anticiapator dict --TODO

~~Add in Metadata dictionary interaction and functionality: likely involving big update to megametadata~~ --TODO

~~introduce data spoofing elements to mimic data types with random data~~ --TODO

~~constrain the spoof generation to the features of the underlying data, min max, type combos etc ~~--TODO

Add further tests to the output of the spoofing functionality --TODO


## New Spoofing system

The new spoofing mechanism planned will ideally remove the breaking cases where column wise spoofing was introducing illegal combinations of values, or multiples of some combinations where those combinations were unique in the data. 

It will summarise at all the nominal variables, and for each combination it will calculate a random value for all value columns. This will form the first phase of the spoof. 

If there is sufficient columns in the first phase, it will be sampled down to 100 by default

if there is not, the mechanism will run again, binding the additional rows in all cases where the combination count is greater than 1.

This process will repeat until either 100+ rows have been spoofed or there is no more combinations with sufficient count to be included

Functions needed:

- ~~Qualifier function which can identify the ordinal columns in a way  which would be accepted by vars in summarise at/ alternatively a boolean function which can be accepted by summarise if. ~~

- ~~Random generator function which can act on a grouped column. ~~

- wrapper function which applies the above process and exploits the above function to create a spoofed dataset


## Overse Mechanics

The Overse project is an attempt to add tooling to an R analysis or investigative workflow. The tooling has been concieved as a mechanism to remove the occurance of times when through time. policy changes or employment changes, the meaning and functionality of an analysis becomes lost. It will do this by filling a process with documentation, and making it easy to act with moderation in terms of access to the full database. 

The underlying data may move, and there's no guarantee even the original author will be able to smoothly apply the work done in that project to another one without any working examples.

You may want to build in tests to functions, but aren't comfortable/allowed to embed sensitive data in your functions.

An author may leave, and all the background work put into figuring out the underlying methodology behind a variable may become lost. And even if documented, it may go missing. 
