---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# UltraSpoofR

The goal of UltraSpoofR is to modify the typical workflow such that the raw genuine data can be disconnected from the bulk of the workflow. It will do this by providing a new data object, which has an authenticated link to the actual data, along with a data dictionary to describe that data and a reasonable spoof of that data. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


## TODOs

Add in regex case insensitivity to type argument of the anticiapator dict --TODO
Add in Metadata dictionary interaction and functionality: likely involving big update to megametadata --TODO
introduce data spoofing elements to mimic data types with random data --TODO
constrain the spoof generation to the features of the underlying data, min max, type combos etc --TODO


## New Spoofing system

The new spoofing mechanism planned will ideally remove the breaking cases where column wise spoofing was introducing illegal combinations of values, or multiples of some combinations where those combinations were unique in the data. 

It will summarise at all the nominal variables, and for each combination it will calculate a random value for all value columns. This will form the first phase of the spoof. 

If there is sufficient columns in the first phase, it will be sampled down to 100 by default

if there is not, the mechanism will run again, binding the additional rows in all cases where the combination count is greater than 1.

This process will repeat until either 100+ rows have been spoofed or there is no more combinations with sufficient count to be included

Functions needed:

- Qualifier function which can identify the ordinal columns in a way  which would be accepted by vars in summarise at/ alternatively a boolean function which can be accepted by summarise if. 

- Random generator function which can act on a grouped column. 

- wrapper function which applies the above process and exploits the above function to create a spoofed dataset
